Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram

### 2015-06-10 papers/MbhMsph/mm.tex
arcetri wed

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{color}

@@

\shorttitle{Early and late $M_{\rm BH} - M_{\rm *,sph}$ sequence}
\shortauthors{Savorgnan et al.}

@@

\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}

@@

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$.
At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper \emph{late-type sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 

@@

@@

Most of these factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 

@@

we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes 

@@

and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late-type) galaxies.

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

 Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\
                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are enclosed with a square. 
The black solid line shows the BCES bisector linear regression for the spheroids that have $n_{\rm sph} \geq 2$, 
such that $M_{\rm BH} \propto L_{\rm sph}^{1.25 \pm 0.13}$. }
\label{fig:pseudob}
\end{center}
\end{figure}

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\
                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

$n>2$ (43)             & BCES $(Y|X)$      & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & BCES $(X|Y)$      & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.10$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]

Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.32 \pm 0.11$  & $-25.73$ & $-$    & $0.42$ \\
                   & BCES $(X|Y)$   & $9.06 \pm 0.12$ & $-0.65 \pm 0.12$  & $-25.73$ & $-$    & $0.61$ \\
                   & BCES Bisector  & $9.06 \pm 0.10$ & $-0.47 \pm 0.08$  & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
                   & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.16$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]

S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & BCES $(X|Y)$   & $7.71 \pm 0.14$ & $-0.86 \pm 0.16$ & $-22.92$ & $-$    & $0.93$ \\
              & BCES Bisector  & $7.71 \pm 0.10$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
              & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.15$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]

>>>>

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{color}
\usepackage{hyperref}

@@

%\shorttitle{Early and late $M_{\rm BH} - M_{\rm *,sph}$ sequence}
\shorttitle{Red and blue $M_{\rm BH} - M_{\rm *,sph}$ sequence}

\shortauthors{Savorgnan et al.}

@@

%\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
\title{Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}

@@

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight %\emph{early-type sequence} 
\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$.
At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
\emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

Here we investigate in more detail %substructure in 
the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 

@@

It is worth stressing that, contrary to common knowledge, the majority of ``elliptical'' galaxies contain disks,
i.e.~they are not single-component spheroidal systems.

@@

Most of these factors are not included in popular 2D fitting codes which report only the {\bf statistical} errors associated with their fitted parameters. 

@@

we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes\footnote{The 
value of the intrinsic scatter obviously depends also on the size of the uncertainties associated with the black hole masses. 
However, black hole masses and their uncertainties have been estimated by various authors using different methods, 
thus we have limited to no control on their values.}  

@@

and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies\footnote{The majority 
of our early-type galaxies are elliptical galaxies, some of which have a bulge-to-total ratio close to 1 ($L_{\rm gal} \simeq L_{\rm sph}$).
One might wonder whether this constitutes a bias in our analysis.
However, we checked that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ 
not only for early-type (elliptical + lenticular) galaxies, 
but also for lenticular galaxies only. }, 
but not for all (early+late-type) galaxies.

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\ [0.5em]
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

 Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\ [0.5em]
                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude (as in Figure \ref{fig:mbhmagsph}). 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are enclosed with a square. 
The black solid line shows the BCES bisector linear regression for the spheroids that have $n_{\rm sph} \geq 2$, 
such that $M_{\rm BH} \propto L_{\rm sph}^{1.25 \pm 0.13}$. }
\label{fig:pseudob}
\end{center}
\end{figure}

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\ [0.5em]
                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\ [0.5em]
                       & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

$n>2$ (43)             & BCES $(Y|X)$      & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\ [0.5em]
                       & BCES $(X|Y)$      & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\ [0.5em]
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.10$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]

Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.32 \pm 0.11$  & $-25.73$ & $-$    & $0.42$ \\
                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\ [0.5em]
                   & BCES $(X|Y)$   & $9.06 \pm 0.12$ & $-0.65 \pm 0.12$  & $-25.73$ & $-$    & $0.61$ \\
                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\ [0.5em]
                   & BCES Bisector  & $9.06 \pm 0.10$ & $-0.47 \pm 0.08$  & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.16$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]

S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\ [0.5em]
              & BCES $(X|Y)$   & $7.71 \pm 0.14$ & $-0.86 \pm 0.16$ & $-22.92$ & $-$    & $0.93$ \\
              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\ [0.5em]
              & BCES Bisector  & $7.71 \pm 0.10$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.15$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
